Understanding Vulnerability: An Analysis of Toronto Police Service's Annual Statistical Report on Crimes Against the Person(2014-2022)

### 2024-01-25 output/paper/paper.qmd
updated paper.qmd and moving sketches

@@

# Read data
crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
column_specifications <- spec(crime_data)
# Calculate total number of crimes reported per year
total_counts <- aggregate(COUNT_ ~ REPORT_YEAR, data = crime_data, sum)  
# Create a bar graph using ggplot2 
ggplot(total_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_)) +   
  geom_bar(stat = "identity", fill = "blue", alpha = 0.7) + 
   geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
  labs(      
       x = "Year",        
       y = "Total Number of Crimes") +  
  scale_y_continuous(breaks = seq(0, max(total_counts$COUNT_), by = 2000)) + # Set y-axis breaks
  theme_minimal()

@@

# Create a bar graph using ggplot2 with subtype on the bars
ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-3
#| fig-cap: "Graph of total number of victims per year by sex"

@@

# Create a scatter plot using ggplot2 with sex on the x-axis
ggplot(sex_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = SEX)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(sex_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("F" = "blue", "M" = "red", "U" = "brown"),
                     labels = c("F" = "Female", "M" = "Male", "U" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-4
#| fig-cap: "Graph of total number of victims per year by age group"

@@

# Create a line graph using ggplot2 with age_group on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
  geom_line(linewidth = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total Number of Crimes") +
  scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("Youth" = "blue", "Child" = "red", "Adult" = "green", "Unknown" = "purple"),
                     labels = c("Youth" = "Youth", "Child" = "Child", "Adult" = "Adult", "Unknown" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-5
#| fig-cap: "Graph of total number of adult victims per year by age cohort"

@@

# Create a line graph using ggplot2 with age cohort on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_COHORT, group = AGE_COHORT)) +
  geom_line(linewidth = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
    x = "Year",
    y = "Total Number of Crimes"
  ) +
  scale_color_manual(values = c(
    "18 to 24" = "blue", "25 to 34" = "red", "35 to 44" = "green", 
    "45 to 54" = "purple", "55 to 64" = "orange", "65+" = "pink"
  )) +  # Specify colors
  theme_minimal()

>>>>

Our analysis examines the trends about victims of crimes against the person reported to the Toronto Police from 2014-2022, revealing insights about the nature of crime and help us understand the factors contributing to vulnerability towards such crimes.

@@

# Read data
crime_data <- read_csv("output/data/edited_data.csv",show_col_types = FALSE) 
column_specifications <- spec(crime_data)
# Calculate total number of crimes reported per year
total_counts <- aggregate(COUNT_ ~ REPORT_YEAR, data = crime_data, sum)  
# Create a bar graph using ggplot2 
ggplot(total_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_)) +   
  geom_bar(stat = "identity", fill = "blue", alpha = 0.7) + 
   geom_line(aes(group = 1), stat = "smooth", method = "lm", se = FALSE, color = "red", linetype = "solid") +  # Add trendline
  labs(      
       x = "Year",        
       y = "Total victims") +  
  scale_y_continuous(breaks = seq(0, max(total_counts$COUNT_), by = 2000)) + # Set y-axis breaks
  theme_minimal()

@@

# Create a bar graph using ggplot2 with subtype on the bars
ggplot(subtype_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, fill = SUBTYPE)) +
  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total victims") +
  scale_y_continuous(breaks = seq(0, max(subtype_counts$COUNT_), by = 2000)) +
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-3
#| fig-cap: "Graph of total number of victims per year by sex (2014-2022)"

@@

# Create a scatter plot using ggplot2 with sex on the x-axis
ggplot(sex_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = SEX)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total victims") +
  scale_y_continuous(breaks = seq(0, max(sex_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("F" = "blue", "M" = "red", "U" = "brown"),
                     labels = c("F" = "Female", "M" = "Male", "U" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-4
#| fig-cap: "Graph of total number of victims per year by age group (2014-2022)"

@@

# Create a line graph using ggplot2 with age_group on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_GROUP, group = AGE_GROUP)) +
  geom_line(linewidth = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
       x = "Year",
       y = "Total victims") +
  scale_y_continuous(breaks = seq(0, max(age_counts$COUNT_), by = 2000)) +
  scale_color_manual(values = c("Youth" = "blue", "Child" = "red", "Adult" = "green", "Unknown" = "purple"),
                     labels = c("Youth" = "Youth", "Child" = "Child", "Adult" = "Adult", "Unknown" = "Unknown")) +  # Specify colors and labels
  theme_minimal()

@@

```{r}
#| eval: true
#| warning: false
#| label: fig-5
#| fig-cap: "Graph of total number of adult victims per year by age cohort (2014-2022)"

@@

# Create a line graph using ggplot2 with age cohort on the x-axis
ggplot(age_counts, aes(x = as.factor(REPORT_YEAR), y = COUNT_, color = AGE_COHORT, group = AGE_COHORT)) +
  geom_line(linewidth = 1, alpha = 0.7) +
  geom_point(size = 3, alpha = 0.7) +
  labs(
    x = "Year",
    y = "Total victims"
  ) +
  scale_color_manual(values = c(
    "18 to 24" = "blue", "25 to 34" = "red", "35 to 44" = "green", 
    "45 to 54" = "purple", "55 to 64" = "orange", "65+" = "pink"
  )) +  # Specify colors
  theme_minimal()
